Changes in Mobility and Site Occupation during the Late Pleistocene in Korea

### 2020-08-17 analysis/paper/paper.Rmd
updating the figures

```{r}
#Volume and artefact counts to get density over time. 
kasv_tidy <- 
kasv %>% 
  t %>% 
  as_tibble() %>% 
  setNames(as.character(.[1,])) %>% 
  .[-1,] %>% 
  mutate_all(parse_number) %>% 
  mutate(artefact_density = total_artifacts / volume,
         sites = names(kasv)[-1])

ggplot(kasv_tidy,
       aes(date_age,
           artefact_density)) +
  geom_point(aes(size = total_artifacts)) +
  geom_text_repel(aes(label = sites),
                  nudge_x = 0.25, 
                  nudge_y = 0.25) +
  ylab("Artifact density") +
  xlab("Age of assemblage (ka)") +
  scale_size_continuous(name = "Total number\nof artifacts")  +
  theme_minimal(base_size = 16)

# without site name
ggplot(kasv_tidy,
       aes(date_age / 1000,
           artefact_density)) +
  geom_point(aes(size = total_artifacts)) +
  ylab("Artefact density") +
  xlab("Age of assemblage (ka)") + 
  scale_size_continuous(name = "Total number\nof artifacts")  +
  theme_minimal(base_size = 16)
ggsave("figures/age-by-density.png")

@@

@@

#k_kas_sites_sheets <- map(p_sheets, ~path %>% )

>>>>

```{r}
#Volume and artefact counts to get density over time. 
kasv_tidy <- 
kasv %>% 
  t %>% 
  as_tibble() %>% 
  setNames(as.character(.[1,])) %>% 
  .[-1,] %>% 
  mutate_all(parse_number) %>% 
  mutate(artefact_density = total_artifacts / volume,
         sites = names(kasv)[-1]) %>% 
  left_join(mydata, by = c('sites' = 'site_name' )) %>% 
  mutate(has_sp = ifelse(is.na(SP.), "no", "yes"))

density_sp_sub_plot <- 
ggplot(kasv_tidy,
       aes(has_sp, 
           artefact_density)) +
  geom_boxplot() +
  theme_bw(base_size = 8)  +
  labs(x = "Stemmed points present",
       y = "Artefact density")

density_sp_main_plot <- 
ggplot(kasv_tidy,
       aes(date_age / 1000,
           artefact_density)) +
  geom_point(aes(size = total_artifacts,
                 colour = has_sp)) +
  ylab("Artefact density") +
  xlab("Age of assemblage (ka)") + 
  #geom_smooth(method = "lm") + 
  scale_size_continuous(name = "Total number\nof artifacts")  +
  scale_color_viridis_d(name = "Contains\nstemmed\npoints?") +
  theme_minimal(base_size = 16)  #+
  #geom_text_repel(aes(label = sites),
  #                nudge_x = 0.25, 
  #                nudge_y = 0.25)

# https://wilkelab.org/cowplot/articles/drawing_with_on_plots.html
library(cowplot)
ggdraw(density_sp_main_plot) +
  draw_plot(density_sp_sub_plot, 
            .375, .67, 
            .25, .25)

ggsave("figures/age-by-density.png")
```

@@

```{r}
# retouch, density, age
Assemblage_info <- read_csv(here::here("analysis/data/raw_data/Assemblage_info.csv"))

Assemblage_info_retouch_density_ages <- 
Assemblage_info %>% 
  pivot_longer(-X1, 
               names_to = "sites") %>% 
  left_join(kasv_tidy)

Assemblage_info_retouch_density_ages_prop <- 
Assemblage_info_retouch_density_ages %>% 
     filter(!X1 %in% c("debris", 
                     "unkown", 
                     "pebble",  
                     "metate", 
                     "flake",
                     "unfinished",
                     "ground",
                     "blank"
                     )) %>% 
  group_by(sites) %>% 
  mutate(prop_retouched = sum(value, na.rm = TRUE) / total_artifacts) %>% 
  arrange(sites) %>% 
  select(-X1, -value) %>% 
  distinct_all()

# retouch over time
retouch_over_time_subplot <- 
ggplot(Assemblage_info_retouch_density_ages_prop,
       aes(date_age / 1000,
           prop_retouched)) +
  geom_point(size = 3, 
             colour = "grey80") +
  labs(x = "Age of assemblage (ka)",
       y = "Proportion retouched") +
  theme_bw(base_size = 6)

# compute correlation
kas_sites_retouch_density_corr <- 
cor.test(Assemblage_info_retouch_density_ages_prop$prop_retouched,
         Assemblage_info_retouch_density_ages_prop$artefact_density)

r_value <- unname(kas_sites_retouch_density_corr$estimate)
p_value <- unname(kas_sites_retouch_density_corr$p.value )
t_value <- unname(kas_sites_retouch_density_corr$statistic )
df_value <- unname(kas_sites_retouch_density_corr$parameter )

size <-  8
Assemblage_info_retouch_density_ages_prop_main_plot <- 
ggplot(Assemblage_info_retouch_density_ages_prop,
       aes(artefact_density,
           prop_retouched
           )) +
  geom_point(aes(colour = date_age / 1000,
                 size = total_artifacts,
                 shape = has_sp)) +
 # geom_text_repel(aes(label = sites),
 #                 nudge_x = 0.075, 
 #                 nudge_y = -0.075,
 #                 size = 5) +
  geom_smooth(alpha = 0.2,
              method = "lm") +
  scale_y_log10(limits = c(0.001, 1),
                labels = scales::comma_format(accuracy = 0.001)) +
  scale_x_log10(limits = c(0.001, 10),
                labels = scales::comma_format(accuracy = 0.001)) +
  theme_minimal(base_size = 12) +
  scale_shape_discrete("Contains\nstemmed\npoints?") +
  scale_size("Total number\nof artifacts") +
  scale_color_viridis_c(name = "Age of\nassemblage (ka)") +
  xlab("Artifact volumetric density") +
  ylab("Proportion of retouched pieces") +
  annotate("text",
           x = 0.005,
           y = 0.7,
           label = "Curated",
           size = size -2,
           colour = "grey50") +
    annotate("text",
           x = 5,
           y = 0.01,
           label = "Expedient",
           size = size -2,
           colour = "grey50") +
    annotate("text",
           x = 0.03,
           y = 0.02,
           label = glue('r = {round(r_value, 3)}\nt({df_value}) =  {round(t_value, 3)}, p = {round(p_value, 3)}'),
           size = size - 2,
           colour = "grey50")

library(cowplot)
ggdraw(Assemblage_info_retouch_density_ages_prop_main_plot) +
  draw_plot(retouch_over_time_subplot, 
            .1, .1, 
            .35, .25)

@@

k_kas_sites_sheets <- map(p_sheets, ~path %>% read_excel )
